A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-09 final project/Manuscript.Rmd
Figured out how to print the R file

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")
```

@@

```{r source, code=readLines("CoIL.R")}
```

>>>>

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")

library(tidyverse)

# Thank you Stack Overflow!
# A Prefix nulling hook.

# Make sure to keep the default for normal processing.
default_output_hook <- knitr::knit_hooks$get("output")

# Output hooks handle normal R console output.
knitr::knit_hooks$set( output = function(x, options) {

  comment <- knitr::opts_current$get("comment")
  if( is.na(comment) ) comment <- ""
  can_null <- grepl( paste0( comment, "\\s*\\[\\d?\\]" ),
                     x, perl = TRUE)
  do_null <- isTRUE( knitr::opts_current$get("null_prefix") )
  if( can_null && do_null ) {
    # By default R print output aligns at the right brace.
    align_index <- regexpr( "\\]", x )[1] - 1
    # Two cases: start or newline
    re <- paste0( "^.{", align_index, "}\\]")
    rep <- comment
    x <- gsub( re, rep,  x )
    re <- paste0( "\\\n.{", align_index, "}\\]")
    rep <- paste0( "\n", comment )
    x <- gsub( re, rep,  x )
  }

  default_output_hook( x, options )

})
knitr::opts_template$set("kill_prefix"=list(comment=NA, null_prefix=TRUE))
```

@@

<code>
```{r, null_prefix = TRUE, comment=NA}
conn <- file("CoIL.r", open="r")
lines <- readLines(conn)
for (i in 1:length(lines)){
  cat(lines[i], "\n")
}
close(conn)
```
</code>

### 2019-11-09 final project/Manuscript.tex
Figured out how to print the R file

>>>>

\begin{verbatim}
# CoIL Challenge Source Code 
library(tidyverse) 
# Download the data sets from UCI if they are not present 
url <- "https://archive.ics.uci.edu/ml/machine-learning-databases/tic-mld/" 
files <- c("ticdata2000.txt", "ticeval2000.txt", "tictgts2000.txt") 
for (file_name in files) { 
  file_path <- paste0("data/", file_name) 
  file_url <- paste0(url, file_name) 
  if (!file.exists(file_path)) { 
    message(paste("Downloading", file_name)) 
    download.file(file_url, file_path) 
  } 
} 
# Read in the data 
df <- read.delim("data/ticdata2000.txt", header = FALSE) 
names(df) <- c("MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", 
               "MGODRK", "MGODPR", "MGODOV", "MGODGE", "MRELGE", "MRELSA", 
               "MRELOV", "MFALLEEN", "MFGEKIND", "MFWEKIND", "MOPLHOOG", 
               "MOPLMIDD", "MOPLLAAG", "MBERHOOG", "MBERZELF", "MBERBOER", 
               "MBERMIDD", "MBERARBG", "MBERARBO", "MSKA", "MSKB1", "MSKB2", 
               "MSKC", "MSKD", "MHHUUR", "MHKOOP", "MAUT1", "MAUT2", "MAUT0", 
               "MZFONDS", "MZPART", "MINKM30", "MINK3045", "MINK4575", 
               "MINK7512", "MINK123M", "MINKGEM", "MKOOPKLA", "PWAPART", 
               "PWABEDR", "PWALAND", "PPERSAUT", "PBESAUT", "PMOTSCO", 
               "PVRAAUT",  "PAANHANG", "PTRACTOR", "PWERKT", "PBROM", "PLEVEN", 
               "PPERSONG", "PGEZONG", "PWAOREG", "PBRAND", "PZEILPL", 
               "PPLEZIER", "PFIETS", "PINBOED", "PBYSTAND", "AWAPART", 
               "AWABEDR", "AWALAND", "APERSAUT", "ABESAUT", "AMOTSCO", 
               "AVRAAUT", "AAANHANG", "ATRACTOR", "AWERKT", "ABROM", "ALEVEN", 
               "APERSONG", "AGEZONG", "AWAOREG",  "ABRAND", "AZEILPL", 
               "APLEZIER", "AFIETS", "AINBOED", "ABYSTAND", "CARAVAN") 
eval <- read.delim("data/ticeval2000.txt", header = FALSE) 
temp <- read.delim("data/tictgts2000.txt", header = FALSE) 
eval$CARAVAN <- temp$V1 
names(eval) <- names(df) 
\end{verbatim}
